Local to Global Mariculture Modelling

### 2025-07-23 index.qmd
Dirs fix

# Filenames
farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
species_params_file <- file.path(output_species_data_path, "species_params.qs")
pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
sens_results_files <- file.path(output_sens_data_path) %>% 
    list.files(full.names = T) %>% 
    str_subset("results")

species_params <- qread(species_params_file)
pop_params <- qread(pop_params_file)

feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", "P" = "darkred", 
  "carbohydrates" = "steelblue", "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
)
```

>>>>

# Filenames
# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))

species_params <- find_read(output_species_data_path, "species_params")
pop_params <- find_read(output_species_data_path, "pop_params")

feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", "P" = "darkred", 
  "carbohydrates" = "steelblue", "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"

# Model functioning

## Population and biomass

```{r raw biomass and weight data}
weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
biomass_cohort <- find_read(output_model_cohort_path, "biomass_stat_all_farms")
```
)
```
